---
title: "Package catalog"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", echo = FALSE,
  warning = FALSE, message = FALSE
)
```

```{r}
library(owdata)
library(DT)

pk <- owd_packages()
harvested <- format(getFromNamespace("owd_active_catalog", "owdata")()$meta$harvest_date)

link <- function(text, url) {
  ifelse(is.na(url) | is.na(text), text, sprintf('<a href="%s">%s</a>', url, text))
}
badge <- function(tier, legacy) {
  cls <- c(dev = "secondary", candidate = "warning", catalogued = "success")[as.character(tier)]
  out <- sprintf('<span class="badge bg-%s">%s</span>', cls, tier)
  ifelse(
    legacy,
    paste(out, '<span class="badge bg-light text-dark" title="Published with a DOI before the 2026 review standard">pre-2026 standard</span>'),
    out
  )
}
```

The table lists every openwashdata package in the catalogued and candidate tiers, harvested from the openwashdata GitHub organization on `r harvested`. Catalogued packages have passed review and carry a Zenodo DOI. Candidate packages have requested review by reaching version 0.1.0 and are shown unreviewed. Packages marked "pre-2026 standard" were published with a DOI before the current review policy existed; see the [versioning policy](versioning-policy.html).

## Catalogued and candidate packages

```{r}
main <- pk[pk$tier %in% c("catalogued", "candidate"), ]
datatable(
  data.frame(
    Package = link(main$pkg_name, main$url_docs),
    Tier = badge(main$tier, main$legacy),
    Title = main$title,
    Version = main$version,
    Datasets = main$n_datasets,
    DOI = link(main$doi, ifelse(is.na(main$doi), NA, paste0("https://doi.org/", main$doi))),
    GitHub = link("repo", main$url_github),
    check.names = FALSE
  ),
  escape = FALSE, rownames = FALSE, filter = "top",
  options = list(pageLength = 25, order = list(list(1, "desc")))
)
```

## Packages in development

Packages below version 0.1.0 are listed for transparency. Their datasets and variables are not part of the catalog until they reach the candidate tier.

<details>
<summary>Show packages in development</summary>

```{r}
dev <- pk[pk$tier == "dev", ]
datatable(
  data.frame(
    Package = link(dev$pkg_name, dev$url_github),
    Title = dev$title,
    Version = dev$version,
    `Last commit` = dev$last_commit,
    check.names = FALSE
  ),
  escape = FALSE, rownames = FALSE,
  options = list(pageLength = 10)
)
```

</details>
